Borel regularity for ODEs and thimble integrals

### 2023-07-21 exp-resurgence.tex

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. \textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. \textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$.

The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
\end{defn}
\begin{defn}\label{def:unif-gevrey-asymp}
On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey-asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
\end{defn}
To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.

\begin{enumerate}[start=4]
\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$. It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
\end{enumerate}

@@

\begin{align*}
\mathcal{P} & = \sum_j^d f_j \frac{\partial}{\partial z}^j \\
& = \sum_j^d f_j \left(-\frac{1}{w^2} \frac{\partial}{\partial w}\right)^j\\
&=  \sum_j^d \tilde{f}_j \frac{\partial}{\partial w}^j
\end{align*}
where $w=1/z$.  if $\tilde{f}_j $ has a pole of order at most $d-j$ at 0 then it's regular singular, otherwise it's irregular. The relevant term should be
\[ \left(\frac{P_d}{w^{2d}} + \frac{R_d(w)}{w^{2d-2}}\right) \left(\frac{\partial}{\partial w}\right)^d , \]
corresponding to the quadratic differential $dw^2/w^{2d}$, whose trajectories form $2(d-1)$ half-planes around $\infty$ (see Bridgeland \& Smith's ``Quadratic differential as stability conditions,'' Figure~10).

@@

Classically it has been proved that the formal solutions $\series{\Psi}_j$ in \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Check references]}. Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.

However, can we find a distinguished basis for solutions in a purely analytic way? This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$. In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame \textcolor{magenta}{[reference-see Sauzin-Mitchi or Delabere book]}, but it is not a constructive method (see Balser chap. 14). Conversely, we can explicitly build a distinguished basis of analytic solutions:

@@

\begin{equation}
\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^dR_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
\end{equation}

such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
\end{theorem}

@@

In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2}: on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$. Then, the theory of multi-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

\begin{remark}
There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}. Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]}. It can indeed be seen as a consequence of ``resurgence'' of the ODE. Our results show how to build a frame of solutions, analytically in the Borel plane. Furthermore, it shows we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$. From the uniqueness result of Theorem~\ref{thm1}, we get a frame of analytic solutions equivalent to \'Ecalle's ones. 
\end{remark}

\begin{remark}
Although, in our proof, we use multi-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane). \textcolor{magenta}{[Is it possible to prove Borel regularity without proving Borel summability? For instance, can we argue that $\psi_j$ being the unique solution of (IE) with a certain behavior is enough to say that it is the sum of $\series{\psi}_j$? Check carefully the argument of multi-summability]} 
\end{remark}

\color{gray}
\begin{itemize}
\item Can we see there exists a distinguished basis in a purely analytic way? YES. [Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
\end{itemize}
\begin{itemize}
\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$. (proof based on existence theorem \ref{frac_int_exist})
\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially. Then this is the only solution that can be expressed as a Laplace transform. [Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]

\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.

\begin{center}
\begin{tikzcd}
& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
& & IE & & \\
\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
\end{tikzcd}
\end{center}

where the arrow in red are a consequence of multisummability. In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones. On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
\item  
there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
\item  M.A.E.T. says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation. Our method uses just Laplace transform. 
\item How do we know we are picking the same frame? from properties of Laplace transform we get solution asymptotics to Poincar\'e frame. From uniqueness result we get a frame equivalent to Ecalle's frame. 
\item multi-summability is a regularity result starting form the formal solution in the $z$-plane. Borel regularity is instead based on the analytic solution in the $z$-plane. The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.   
\end{itemize}

\color{DarkBlue}

@@

\begin{itemize}
\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
\begin{itemize}
\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
\end{itemize} 
\item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial. His proof uses microlocal analysis and classical results due to Varchenko. In the same algebraic setting, Malgrange states the Borel regularity result Theorem 6 \cite{Malgrange22} 
\item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}
\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
\begin{equation}
I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
\end{equation}

then the following diagram is commutative
\begin{equation}
\begin{tikzcd}
I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
& \\
\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
\end{tikzcd}
\end{equation}
\begin{itemize}
\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
\item A corollary of [Thm 4] is the fractional derivative formula.
\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
\begin{equation}
mmm
\end{equation} 
\end{itemize}
\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim). See also the argument of KS21 sec 6.2 in the framework of analytic WCFs. 
\begin{itemize}
\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
\end{itemize}
\end{itemize}

\color{DarkGreen}
We will restrict to $1$-dimensional thimble integrals, and in this special case we will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.  
Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$. Suppose $X$ is of {\em meromorphic type}, meaning that we got it by puncturing a compact Riemann surface $\overline{X}$ at finitely many points, and $\nu$ has a pole at each puncture. A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$.

Take another meromorphic-type translation surface $B$ and a holomorphic Morse\footnote{This condition means that the critical points of $f$ are isolated (the compactness of $\overline{X}$ guarantees this) and the 2-jet of $f$ is non-zero at every critical point.} map $f \maps \overline{X} \to \overline{B}$ \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}. Suppose every singularity of $B$ is a critical value of $f$. \textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series. How to handle the Orr–Sommerfeld functions (DLMF~\S 9.13)? We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]} For each critical point $p$, let $\Gamma_p$ be the ray going rightward from $f(p)$, and let $\zeta_p$ be the translation coordinate around $\Gamma_p$ which vanishes at $f(p)$. These are well-defined as long as $\Gamma_p$ misses the critical values of $f$. The preimage $f^{-1}(\Gamma_p)$ is a bunch of disjoint curves, as long as $\Gamma_p$ misses the other critical values of $f$. The \textcolor{red}{\em Lefschetz thimble} $\Lambda_p$ is the component of $f^{-1}(\Gamma_p)$ that goes through $p$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_p$. \textcolor{red}{Can we say that in $1$-dimension there the two definitions of thimble integrals are actually the same?} The {\em thimble integral}
\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
is a holomorphic function on the right half-plane parametrized by $z$, and it turns out to be Borel regular.

\textbf{[Talk about exponential integrals and their decomposition into thimble integrals.]}

>>>>

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. \textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. \textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$.

The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function \textcolor{orange}{that vanishes at $\infty$ [if it vanishes at $\infty$ it sent to zero, so why this assumption?]} to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ (see \cite[Theorem~C.11]{nikolaev2023existence}).
\end{defn}
\begin{defn}\label{def:unif-gevrey-asymp}
On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey-asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
\end{defn}
To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.

\begin{enumerate}[start=4]
\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$. It turns out that $\hat{\Phi}$ is not only asymptotic to $\series{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
\end{enumerate}

@@

\begin{align*}
\mathcal{P} & = \sum_j^d f_j \frac{\partial}{\partial z}^j \\
& = \sum_j^d f_j \left(-\frac{1}{w^2} \frac{\partial}{\partial w}\right)^j\\
&=  \sum_j^d \tilde{f}_j \frac{\partial}{\partial w}^j
\end{align*}
where $w=1/z$.  if $\tilde{f}_j $ has a pole of order at most $d-j$ at 0 then it's regular singular, otherwise it's irregular. The relevant term should be
\color{Tan}
\[ \left(\frac{P_d}{w^{2d}} + \frac{R_d(w)}{w^{2d-2}}\right) \left(\frac{\partial}{\partial w}\right)^d , \]
\color{DarkTurquoise}
\[ \frac{P_d}{w^{2d}}  \left(\frac{\partial}{\partial w}\right)^d , \]
corresponding to the quadratic differential $dw^2/w^{2d}$, whose trajectories form $2(d-1)$ half-planes around $\infty$ (see Bridgeland \& Smith's ``Quadratic differential as stability conditions,'' Figure~10).

@@

Classically it has been proved that the formal solutions $\series{\Psi}_j$ in \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Braaksma,Loday-Richaud, check]}. Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.

However, can we find a distinguished basis for solutions in a purely analytic way? This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$. In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}). Conversely, we can explicitly build a distinguished basis of analytic solutions:

@@

\begin{equation}
\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
\end{equation}

such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ for a small compact domain $\Omega\subset\C$. 
\end{theorem}

@@

In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2}: on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$. Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

\begin{remark}
There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}. Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]\cite{EcalleIII}\cite{loday-Remy2011}}. It can indeed be seen as a consequence of ``resurgence'' of the ODE. Our results show how to build a frame of solutions, analytically in the Borel plane. Furthermore, it shows we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$. From the uniqueness result of Theorem~\ref{thm1}, we get a frame of analytic solutions equivalent to \'Ecalle's ones. 
\end{remark}

\color{Tan}
\begin{remark}
Although, in our proof, we use $1$-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane). \textcolor{magenta}{[Is it possible to prove Borel regularity without proving Borel summability? For instance, can we argue that $\psi_j$ being the unique solution of (IE) with a certain behavior is enough to say that it is the sum of $\series{\psi}_j$? Check carefully the argument of multi-summability]} 
\end{remark}

\color{magenta}
[Veronica]

Although, in our proof, we adapt an argument by M. Loday-Richaud and P. Remy (see \S 2 in\cite{loday-Remy2011}) to guarantee Borel--Laplace summability, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane). In addition, our proof stresses the importance of the position domain, where in fact the crucial step of the proof is done.

%\color{gray}
%\begin{itemize}
%\item Can we see there exists a distinguished basis in a purely analytic way? YES. %%[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
%\end{itemize}
%\begin{itemize}
%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$. (proof based on existence theorem \ref{frac_int_exist})
%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially. Then this is the only solution that can be expressed as a Laplace transform. [Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]

%\begin{center}
%\begin{tikzcd}
%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
%& & IE & & \\
%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
%\end{tikzcd}
%\end{center}

%where the arrow in red are a consequence of multisummability. In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones. On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
%\item  
%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
%\item  M.A.E.T. says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation. Our method uses just Laplace transform. 
%\item How do we know we are picking the same frame? from properties of Laplace transform we get solution asymptotics to Poincar\'e frame. From uniqueness result we get a frame equivalent to Ecalle's frame. 
%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane. Borel regularity is instead based on the analytic solution in the $z$-plane. The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.   
%\end{itemize}

@@

\color{DarkBlue}
\begin{itemize}
%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
%\begin{itemize}
%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
%\end{itemize} 
\item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial. His proof uses microlocal analysis and classical results due to Varchenko. In the same algebraic setting, Malgrange states the Borel regularity result Theorem 6 \cite{Malgrange22} 
\item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}
\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
%\begin{equation}
%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
%\end{equation}

%then the following diagram is commutative
%\begin{equation}
%\begin{tikzcd}
%I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
%& \\
%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
%\end{tikzcd}
%\end{equation}
\begin{itemize}
%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
\item A corollary of [Thm 4] is the fractional derivative formula.
\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
\begin{equation}
mmm
\end{equation} 
\end{itemize}
\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim). See also the argument of KS21 sec 6.2 in the framework of analytic WCFs. 
\begin{itemize}
\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
\end{itemize}
\end{itemize}
\color{black}

Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\mathbb{A}^1$ be a proper algebraic map with non--degenerate critical points $\alpha_1,...,\alpha_N$ \footnote{Everything we will discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for a fixed $z\in\C$, we are interested in integrals of the form

\[
I(z):=\int_{\mathcal{C}}e^{-zf}\nu
\]

regarded as holomorphic functions in the position domain for a suitable choice of a contour $\mathcal{C}$ and an $N$-form $\nu$. In fact, we introduce homology and cohomology groups $H_{*}^{B,z}$ and $H_{dR,z}^*$ so that the function $I(z)$ will represent the Poincar\'e pairing.

We begin with the definition of $H_{*}^{B,z}$: it is the relative homology group with respect to $zf$, and its definition requires some preliminaries. We follow \cite{pham} and $\S 1$ in \cite{Arnold}. Let us fix $z\in\C$ and $\theta=\arg z$; for every $c>0$ we define 
\begin{align*}
    S_c^+(\theta) &:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\geq c \rbrace\\
    S_c^-(\theta)&:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\leq c \rbrace
\end{align*}
and $H_{*}^{B,z}:=H_{*}(X,f^{-1}(S_c^+(\theta)))$ for $c$ large enough\footnote{In fact $H_{*}^{B,z}$ is defined after taking the projective limit $c\to\infty$ of the chain complex with support $\{A\subset X \text{ closed s.t. } \forall c>0 f^{-1}(S_c^-(\theta))\cup A \text{ is compact }  \}$.}. Moreover, $H_n(X,f^{-1}(S_c^+(\theta)))$ can be identified with the homology of a generic fiber $H_{n-1}(f^{-1}(p_0))$ with $p_0\neq \{\alpha_j\}$. This leads to further identifications:
